%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin]{res} % Use the res.cls style
\pagestyle{plain}
%\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment

\usepackage{hanging}

\setlength{\textwidth}{5.1in} % Text width of the document
\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf David Switzer} % Your name at the top

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\moveleft.5\hoffset\centerline{Truman School of Public Affairs, University of Missouri, 105 Middlebush Hall
} % Your address
\moveleft.5\hoffset\centerline{Columbia, MO 65211}
\moveleft.5\hoffset\centerline{dswitzer70@gmail.com}
\moveleft.5\hoffset\centerline{davidswitzerphd.com}
\moveleft.5\hoffset\centerline{(410) 245-1023}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

%\section{OBJECTIVE}

%A position in the field of computers with special interests in business applications programming, information processing, and management systems.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{ACADEMIC APPOINTMENTS}
\begin{hangparas}{.25in}{1}\textbf{University of Missouri}, Columbia, MO \\
Assistant Professor,  Beginning Fall 2018 \\
Truman School of Public Affairs

\textbf{Florida Atlantic University}, Boca Raton, FL \\
Assistant Professor,  Fall 2017- Spring 2018 \\
School of Public Administration  \end{hangparas}


\section{EDUCATION}
\begin{hangparas}{.25in}{1}\textbf{Texas A\&M University}, College Station, TX \\
PhD Political Science,  2017 \\
\textbf{Dissertation}: \textit{Private Taps, Public Good: Exploring Compliance, Conservation, and Equity in United States Drinking Water} \\
\textbf{Committee}: Manuel P. Teodoro (Chair), Kenneth J. Meier, Cary J. Nederman, Ronald A. Kaiser

\textbf{University of Maryland}, College Park, MD \\
 BA History and Government and Politics, 2012 \end{hangparas}




 %----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------


 \section{PEER REVIEWED ARTICLES}

 \begin{hangparas}{.25in}{1} \textbf{Switzer, David}. Forthcoming. ``Getting off the (Water) Bottle: Constraining or Embracing Individual Liberty in the Pursuit of the Public Interest." \textit{Ethics, Policy \& Environment}.
 
 \textbf{Switzer, David}. Forthcoming. ``Citizen Partisanship, Local Government, and Environmental Policy Implementation." \textit{Urban Affairs Review}.
 
\textbf{Switzer, David} and Manuel P. Teodoro. 2018. ``Class, Race, Ethnicity, and Justice in Safe Drinking Water Compliance." \textit{Social Science Quarterly} 99(2): 524-535.

 Teodoro, Manuel P., Mellie Haider, and \textbf{David Switzer}. 2018. ``U.S. Environmental Policy Implementation on Tribal Lands: Trust, Neglect, and Justice." \textit{Policy Studies Journal} 46(1): 37-59.

\textbf{Switzer, David} and Arnold Vedlitz. 2017. ``Investigating the Determinants and Effects of Local Drought Awareness." \textit{Weather, Climate, and Society} 9(4): 641-657.

\textbf{Switzer, David} and Arnold Vedlitz. 2017. ``Green Colored Lenses: Worldviews and Motivated Reasoning in the Case of Local Water Scarcity." \textit{Environment \& Behavior} 49(7): 719-744.

Teodoro, Manuel P. and \textbf{David Switzer}. 2016. ``Drinking from the Talent Pool: A Resource Theory of Human Capital and Agency Performance." \textit{Public Administration Review} 76(4): 564-575.

\textbf{Switzer, David}, Manuel P. Teodoro, and Stuart Karasik. 2016. ``The Human Capital Resource Challenge: Recognizing and Overcoming Small Utility Workforce Obstacles." \textit{Journal of the American Water Works Association} 108(8): E416-E424.

\hspace{.25in}$\bullet$ 2017 Management \& Leadership Division Best Paper Award, American Water Works Association.

\textbf{Switzer, David} and Nicole Frances Angeli. 2016. ``Human and Non-Human Migration: Understanding Species Introduction and Translocation through Migration Ethics." \textit{Environmental Values} 25(4): 443-463. \end{hangparas}

%----------------------------------------------------------------------------------------
%	WORKING PAPERS
%----------------------------------------------------------------------------------------


 \section{OTHER PUBLICATIONS}

 \begin{hangparas}{.25in}{1} \textbf{Switzer, David} and Manuel P. Teodoro. 2017. ``The Color of Drinking Water: Class, Race, Ethnicity, and Safe Drinking Water Act Compliance." \textit{Journal of the American Water Works Association} 109(9): 40-45.
 
 \textbf{Switzer, David}. 2016. ``Politics and the Environment." Entry in \textit{Global Encyclopedia of Public Administration, Public Policy, and Governance}. Edited by Ali Farazmand.

\textbf{Switzer, David} and Elisabeth Ellis. 2014. ``Shapiro, Ian." Entry in \textit{Wiley-Blackwell Encyclopedia of Political Thought}. Edited by Michael Gibbons.

Teodoro, Manuel P. and \textbf{David Switzer}. 2015. ``Workforce Quality \& Regulatory Compliance in Economically Challenged Regions: Identifying New Strategies." Report to the Workforce Strategies Committee, American Water Works Association. \end{hangparas}

\section{WORKING\\ PAPERS\\}

 \begin{hangparas}{.25in}{1} ``Privatization as Political Decoupling: Water Conservation During the 2015-2017 California Drought." with Manuel P. Teodoro and Youlang Zhang. Invitation to Revise \& Resubmit to \textit{Policy Studies Journal}. 

``Water Conservation in U.S. Water Utilities: A New Measure of Water Rate Progressivity." Under Review.

``Ownership and the Talent Pool: Exploring the Conditional Effect of Human Capital." with Manuel P. Teodoro.

``Partisanship, Responsiveness, and Ownership: Exploring the Differential Responsiveness of Private and Public Water Utilities ."

``What Determines Support for Conservation Water Rates?" with Arnold Vedlitz \end{hangparas}


%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{TEACHING EXPERIENCE}

 \begin{hangparas}{.25in}{1}  Florida Atlantic University: \\
 PAD2258: ``Changing Env. of Society, Business, and Government." x2 \\
 PAD4806: ``State and Local Government Administration."\\
 PAD4704: ``Research Methods for Public Management"
 
Texas A\&M University: \\
 POLS 347: ``Politics of Energy and the Environment."
 
 \end{hangparas}

\section{PROFESSIONAL EXPERIENCE}


\begin{hangparas}{.25in}{1} \textbf{Research Assistant}, Fall 2012-Spring 2017 \\
Department of Political Science \\
 Texas A\&M University

\textbf{Predoctoral Research Associate}, Summer 2015-Fall 2017 \\
Institute for Science, Technology, and Public Policy \\
The George Bush School of Government and Public Service \\
Texas A\&M University

\textbf{Website Design for Workshop} \\
``Machiavelli Between Past and Future," Texas A\&M University \\
February 8-9, 2014 \\
machiavelli500.wordpress.com

\textbf{Lead Student Organizer for Workshop} \\
``Comparative Democratic Theory: A Workshop on Democracy in Inter-Cultural Perspective," Texas A\&M University\\
October 11-12, 2013 \\
comparativedemocracy.wordpress.com

\textbf{Student Organizer for Workshop} \\
``Reconsidering Race: Cross-Disciplinary and Inter-Disciplinary Approaches," Texas A\&M University\\
May 3-4, 2013 \\
reconsideringrace.wordpress.com \end{hangparas}

%----------------------------------------------------------------------------------------
%	CONFERENCE PRESENTATIONS
%----------------------------------------------------------------------------------------



\section{CONFERENCE PRESENTATIONS}

 \begin{hangparas}{.25in}{1}

  ``Issue Severity and Citizen Preferences in Local Water Conservation Policy." Presented at the American Political Science Association Annual Meeting (August 31-September 3, 2017)

 ``Ownership and the Talent Pool: Exploring the Conditional Effect of Human Capital." with Manuel P. Teodoro. Presented at the American Political Science Association Annual Meeting (August 31-September 3, 2017)
 
  ``Public Participation, Responsiveness, and Compliance in Water Utility Privatization." Presented at the American Political Science Association Annual Meeting (September 1-4, 2016)

"Ideology, Inequality, and Water Scarcity in Private and Public Utility Rate Adoption." Presented at the Southern Political Science Association Annual Meeting (January 12-14, 2017)

 ``Public Participation, Responsiveness, and Compliance in Water Utility Privatization." Presented at the American Political Science Association Annual Meeting (September 1-4, 2016)

 ``Environmental Marble Cake: Three Level Federalism in Environmental Compliance." with Manuel P. Teodoro, Mellie Haider, and Youlang Zhang. Presented at the American Political Science Association Annual Meeting (September 1-4, 2016)

 ``Private Taps, Public Goods: Public Participation, Conservation, and Governance in the Privatization of Drinking Water."  Presented at the Western Political Science Association Annual Meeting (March 24-26, 2016)

``Local Issue Severity and Ideological Worldviews: Motivated Reasoning in the Case of Water Scarcity." with Arnold Vedlitz. Presented at the Southern Political Science Association Annual Meeting (January 7-9, 2016) 	

``Sovereignty, Capacity, and Justice: U.S. Environmental Policy under Tribal Governance." with Manuel P. Teodoro and Mellie Haider. Presented at the American Political Science Association Annual Meeting (September 3-6, 2015) 	

``Privatization, Responsiveness, and Environmental Performance: Exploring the Conditional Effect of Participation on SDWA Compliance." Presented at the Public Management Research Association Conference (June 11-13, 2015) 	

``Drinking From the Talent Pool: Human Capital, Organizational Capacity, and Regulatory Complianc.e" with Manuel P. Teodoro. Presented at the American Water Works Association Annual Conference and Exposition June 8-10, 2015) 	

``Do Elections Water Down Regulatory Enforcement?" with Andrew Philips. Presented at the Midwest Political Science Association Annual Meeting (April 15-18, 2015) 	

``Class, Race, Ethnicity, and Justice in Safe Drinking Water Act Compliance and Enforcement." with Manuel P. Teodoro. Presented at the Midwest Political Science Association Annual Meeting (April 15-18, 2015) 	

``Constraining or Embracing Individual Liberty?: The Case of Bottled Water."  Presented at the Western Political Science Association Annual Meeting (April 2-4, 2015) 	

``Drinking from the Talent Pool: Performance, Capacity, and Human Capital as a Resource." with Manuel P. Teodoro. Presented at the Southern Political Science Association Annual Meeting (January 15-17, 2015) 	\end{hangparas}










 %----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	Skills and Development
%----------------------------------------------------------------------------------------

\section{SKILLS \& PROFESSIONAL DEVELOPMENT}

 \begin{hangparas}{.25in}{1} \textbf{Advanced Game Theory}, Summer 2014 \\
 ICPSR Summer Program in Quantitative Methods \\
Taught by James Morrow

\textbf{Hierarchical Linear Modeling}, Summer 2013 \\
 Summer Methods Workshop, Texas A\&M University \\
 Taught by Dave Peterson

\textbf{Technical Skills}: Stata, R, \LaTeX, ArcGIS, HTML	 \end{hangparas}	
 %----------------------------------------------------------------------------------------




%----------------------------------------------------------------------------------------
%	FUNDING & Research Awards
%----------------------------------------------------------------------------------------

\section{FUNDING \& RESEARCH AWARDS}

 \begin{hangparas}{.25in}{1} American Water Works Association, ``Workforce Quality \& Regulatory Compliance in Economically Challenged Regions," \textit{Technical and Educational Council Grant}; 2015 (\$25,000). Staff for Manuel P. Teodoro.

Texas A\&M, College of Liberal Arts, \textit{Professional Development Award}; 2014 (\$3,742).

University of Maryland, College Park Scholars, \textit{Ira Berlin Writing Award}; 2011 (\$50). \end{hangparas}



%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	Profesional membership & SERVICE
%----------------------------------------------------------------------------------------
\section{PROFESSIONAL MEMBERSHIP \& SERVICE}

 \begin{hangparas}{.25in}{1} \textbf{Member}: American Political Science Association, Midwest Political Science Association, Southern Political Science Association, Western Political Science Association, Association for Political Theory, American Water Works Association

\textbf{Discussant}: WPSA 2016

\textbf{Reviewer}: \textit{Nature Climate Change}, \textit{Political Research Quarterly}, \textit{Journal of the American Water Works Association},  \textit{Urban Studies}, \textit{American Journal of Public Health} x2, \textit{Publius: The Journal of Federalism}, \textit{Environmental Values}, \textit{Policy Studies Journal}

\textbf{President}: Texas A\&M Political Science Graduate Students Association, 2015-2016 \end{hangparas}










\end{resume}
\end{document} 